Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-09 ccppabc/text/revision/main.tex
outlines for what needs to be added at the end of Section 3.4. in order to address Ref Report comment #4 (issue #18)

The ABC method of parameter inference has often been viewed as computationally infeasible due to the 
fact that it necessitates a generative forward model for a large number of realizations. However, 
by combining ABC with the PMC sampling method,
%of importance sampling {\bf [APH: the term "importance sampling" has not been defined]}, 
we have a method that efficiently converges 
to give us reliable posteriors of the model parameters. Furthermore, in our analysis, the computational resources 
required for the ABC-PMC inference were comparable to those used in achieving convergence in the 
MCMC Gaussian-Likelihood inference. This is excluding the typically computationally intensive step of 
calculating a covariance matrix estimate. Therefore, we find that ABC-PMC offers a method for parameter
inference in large scale structure studies with a number of advantages we describe above.

>>>>

The ABC method of parameter inference has often been viewed as computationally infeasible due to the 
fact that it necessitates a generative forward model for a large number of realizations. However, 
by combining ABC with the PMC sampling method,
%of importance sampling {\bf [APH: the term "importance sampling" has not been defined]}, 
we have a method that efficiently converges 
to give us reliable posteriors of the model parameters. Furthermore, in our analysis, the computational resources 
required for the ABC-PMC inference were comparable to those used in achieving convergence in the 
MCMC Gaussian-Likelihood inference. This is excluding the typically computationally intensive step of 
calculating a covariance matrix estimate. Therefore, we find that ABC-PMC offers a method for parameter
inference in large scale structure studies with a number of advantages we describe above. 
{\bf \color{darkgreen}
Need discussion of applying ABC to real data. 
\begin{itemize}
\item Computational tractability caveats. The forward models in real data scenarios would have to be much bigger. 
\item They would also have to be better than the ones that are currently used for covariance matrix estimation. 
\item Complexity of systematic effects (mention DESI) 
\item End with how there's still hope because there's developments in fast simulations
\end{itemize}
}
